\textls[-0]{\thetitle}

### 2022-11-11 conclusion.tex
fix broken refs
assorted changes

It is hard to write modular, extensible code and proofs.
We have presented a solution that equips a proof assistant with
linguistic facilities for family polymorphism.
The language design ensures that the expressive power brought by family polymorphism
is in harmony with the strictness of a proof assistant, while incurring
low cognitive overhead and allowing an idiomatic programming experience.
We implement the design via a translation to Coq and demonstrate its applicability
using case studies.
A novel dependent type theory formalizes the core aspects of the language mechanism
and is shown to enjoy consistency and canonicity.
Generalizing the mechanism to support nested family polymorphism and
scaling it to sizable proof engineering efforts make exciting directions for
future work.

>>>>

It is hard to write modular, extensible code and proofs.
We have presented a solution that equips a proof assistant with
linguistic facilities for family polymorphism.
The language design ensures that the expressive power brought by family polymorphism
is in harmony with the strictness of a proof assistant, while incurring
low cognitive overhead and allowing an idiomatic programming experience.
We implement the design via a translation to Coq and demonstrate its applicability
using case studies.
A novel dependent type theory formalizes the essence of the language mechanism
and is shown to enjoy consistency and canonicity.
Generalizing the mechanism to support nested family polymorphism
will make extensibility scale to sizable proof engineering efforts and
thus make exciting directions for future work.

### 2022-11-11 stlc-linkTran-typing.tex
assorted changes

In this appendix, we sketch how to use the ``library'' of linkage
transformers in \TT to inductively construct a linkage that models a
derived family of \lsti{STLC}.

@@

Of note is the two grayed rows. They are constructing a linkage transformer~$h_\beta$
containing the case handlers for \lsti{subst}.
This $h_\beta$ is then appended to $h_3$ as a nested linkage transformer.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\small
\renewcommand*{\arraystretch}{1.25}
\begin{tabular}{|l|l|l|}
\hline
\rowcolor[HTML]{FFFC9E} 
surface-syntax program & $i$      & $\goodInh{\cdot}{h_i}{\lsig_i}{\lsig_i'}$             \\ \hline
\lsti!Family STLCBool!   & 0        & $\InhId$                                             \\ \cline{2-3} 
\lsti!FInductive tm += !       & 1        & $\InhOv{h_0}{\wcode{\wsig_{\texttt{tm}}'}}$                      \\ \cline{2-3} 
\codecomment{existing constructors}   & 2        & $\InhOv{h_1}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$           \\ \cline{2-3} 
\lsti!| tm_true |!\ \;\dadada    & 3        & $\InhExt{h_2}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$          \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!FRecursion subst!\ \;\dadada\ \;\lsti!+=! & $\alpha$ & $\InhId$ \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!  Case tm_true := !\dadada. \lsti! Case !\dadada & $\beta$  & $\InhExt{h_\alpha}{...}$ \\ \cline{2-3} 
\rowcolor[HTML]{FFFFFF} 
\lsti!End subst.!              & 4        & $\InhNest{h_3}{h_\beta}$
  %with $\uparrow^s_3$
  \\ \cline{2-3} 
                          & 5        & $\InhOv{h_4}{\lambda t. \Wrec{\wsig_{\texttt{tm}}'}{t}{"substCases"}}$ \\ \cline{2-3} 
\lsti!FInductive ty += !\dadada. & 6        & ...                                                  \\ \cline{2-3} 
\codecomment{Inherit "env"}   & 7        & $\InhInh{h_6}$
  %with $\uparrow^s_6$
  \\ \cline{2-3} 
\codecomment{Inherit "empty"}   & 8        & $\InhInh{h_7}$
  \\ \cline{2-3} 
\dadada   & \dadada & \dadada
  \\ \hline
\end{tabular}
\end{centered}

>>>>

In this appendix, we sketch how to use the ``library'' of linkage
transformers in \TT to inductively construct a linkage transformer that models a
derived family of \lsti{STLC}.

@@

Most steps are self-explanatory.
Of note is the two grayed rows. They are constructing a linkage transformer~$h_\beta$
containing the case handlers for \lsti{subst}.
This $h_\beta$ is then appended to $h_3$ as a nested linkage transformer.

@@

% Please add the following required packages to your document preamble:
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{centered}
\small
\renewcommand*{\arraystretch}{1.25}
\begin{tabular}{|l|l|l|}
\hline
\rowcolor[HTML]{FFFC9E} 
surface-syntax program & $i$      & $\goodInh{\cdot}{h_i}{\lsig_i}{\lsig_i'}$             \\ \hline
\lsti!Family STLCBool extends STLC.!   & 0        & $\InhId$                                             \\ \cline{2-3} 
\lsti!FInductive tm += !       & 1        & $\InhOv{h_0}{\wcode{\wsig_{\texttt{tm}}'}}$                      \\ \cline{2-3} 
\codecomment{existing constructors}   & 2        & $\InhOv{h_1}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$           \\ \cline{2-3} 
\lsti!| tm_true |!\ \;\dadada    & 3        & $\InhExt{h_2}{\Wsup{\wsig_{\texttt{tm}}'}{\top}{\bot}}$          \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!FRecursion subst!\ \;\dadada\ \;\lsti!+=! & $\alpha$ & $\InhId$ \\ \cline{2-3} 
\rowcolor[HTML]{CDCDCD} 
\lsti!  Case tm_true := !\dadada. \lsti! Case !\dadada & $\beta$  & $\InhExt{h_\alpha}{...}$ \\ \cline{2-3} 
\rowcolor[HTML]{FFFFFF} 
\lsti!End subst.!              & 4        & $\InhNest{h_3}{h_\beta}$
  %with $\uparrow^s_3$
  \\ \cline{2-3} 
                          & 5        & $\InhOv{h_4}{\lambda t. \Wrec{\wsig_{\texttt{tm}}'}{t}{"substCases"}}$ \\ \cline{2-3} 
\lsti!FInductive ty += !\dadada. & 6        & ...                                                  \\ \cline{2-3} 
\codecomment{Inherit "env"}   & 7        & $\InhInh{h_6}$
  %with $\uparrow^s_6$
  \\ \cline{2-3} 
\codecomment{Inherit "empty"}   & 8        & $\InhInh{h_7}$
  \\ \cline{2-3} 
\dadada   & \dadada & \dadada
  \\ \hline
\end{tabular}
\end{centered}
